Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion.tex
resolving edits

\subsubsection{Discrete Preferences}
\label{subsec:discrete}
Discrete preferences by agents are captured by the following
\dkedit{strengthening of Assumption~\ref{A1}},
which states that the agents who are close to tied between
two arms have measure 0:

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
expected payment  bounded above by  
$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
and expected regret bounded above by
%\begin{align*}
\dkedit{$O \left( \frac{\ARMNUM^2}{\MinProb^2}
%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$}.
%  \end{align*}
\end{theorem}

>>>>

\subsubsection{Discrete Preferences}
\label{subsec:discrete}
Discrete preferences by agents are captured by the following
strengthening of Assumption~\ref{A1},
which states that the agents who are close to tied between
two arms have measure 0:

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
expected payment  bounded above by  
$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
and expected regret bounded above by
%\begin{align*}
$O \left( \frac{\ARMNUM^2}{\MinProb^2}
%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
%  \end{align*}
\end{theorem}
